A fight consists of two parties, the attacker and the enemy. We only consider the damage dealt by the attacker on the enemy and not vice versa. In our model the enemy is attacked periodically until its remaining hitpoints are 0. The attack rate is characterized by the \textit{attack period} $T_A$ which varies between weapons.
Once every attack period the enemy is hit and the damage dealt is calulated as follows.
\begin{enumerate}
	\item The game determines if the hit will succeed by some random process which depends on various parameters, such as defensive bonuses of the enemy, offensive bonuses of the attacker and appropriate combat-related stats. We ignore the details of this process and just say the probability of the hit being successful is $a$ calling it the \textit{accuracy}. If the accuracy check fails, the attack is considered a miss and 0 damage is dealt.
	\item If the accuracy check is successful damage roll $M$, a uniformly distributed random integer between 0 and $m$ is chosen, where $m$ is the \textit{maximum hit}. Again, we do not concern ourselves with the specifics of how the max hit is determined. Notice that it is possible for the hit to deal no damage even if the accuracy check succeeds because the damage roll $M$ could be 0.
    \item If $M > H$, where $H$ is the remaining hitpoints of the enemy, the damage is capped to $H$ and the final damage dealt is $\min(M,H)$. This is the overkill effect.
\end{enumerate}

Unlike the damage calculation process, regeneration is not fundamentally random. It happens by periodically incrementing the remaining hitpoints by one until they are full. The period $T_R$ of this healing cycle is called the \emph{regeneration period} and can vary between enemies giving rise to different regeneration rates. At the beginning of a fight the state of the healing cycle can be assumed to be unknown and thus treated as a random variable. This way only the timing of the first heal is random and the rest are perfectly periodic.
